Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-24 prop_iop.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Added...

\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
Every (classical) convex interval-valued probability measure has a
non-empty core. \end{thm}

>>>>

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}
Every (classical) convex interval-valued probability measure has a
non-empty core. \end{thm}

### 2017-03-24 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Added...

\begin{abstract}
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision. {\small \par}
\item [{Method}] We model idea of the finite precision measurement as finite
number of intervals, and replace quantum real-valued probability measures
by interval-valued ones. {\small \par}
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear. {\small \par}
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.{\small \par}
\end{description}
\end{abstract}

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}\left(P\right)=\iota_{0}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{0}\left(x\right)=\begin{cases}
\necess & \text{ if}x=1\text{ ;}\\
\imposs & \text{ if}x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
Because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we have\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)+\bar{f}(0,0,1,1)\nonumber \\
 &  & +\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)+\bar{f}(0,1,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\
 &  & +\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(1,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)+\bar{f}(0,1,1,0)\nonumber \\*
 &  & +\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)+\bar{f}(0,0,1,1)\nonumber \\*
 &  & +\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)+\bar{f}(1,1,1,1)\nonumber \\*
 &  & +\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)+\bar{f}(1,1,1,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)+\bar{f}(1,1,-1,-1)\nonumber \\*
 &  & +\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up equation~\ref{eq:Kernaghan}, we
will have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(-1,1,1,1)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(-1,1,1,1),(1,-1,1,-1),\nonumber \\
 &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied, because each term can either be $\imposs=\left[0,0\right]$
or $\necess=\left[1,1\right]$.\newpage{}

On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
where $\events$ is the set of all projections on a Hilbert space.
On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
Gleason's theorem asserts that every quantum real-valued probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
by a density matrix according to the Born rule. These two extreme
cases can be understood in a broader framework of quantum interval-valued
probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
a quantum IVPM is well-behaved as a usual quantum real-valued probability
measure does.

On the one hand, the Kochen-Specker theorem is equivalent to the non-existence
of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
where $\events$ is the set of all projections on a Hilbert space.
On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
Gleason's theorem asserts that every quantum real-valued probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
by a density matrix according to the Born rule. These two extreme
cases can be understood in a broader framework of quantum interval-valued
probability measure (IVPM)~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
where $\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
When we pick $\mathscr{I}$ as $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
a quantum IVPM is well-behaved as a usual quantum real-valued probability
measure does.

Given any sub-event space~$\events'\subseteq\events$, in order to
qualify how well-behaved a quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
could be, we introduce the notion of core.

\begin{definition}A \emph{core} of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events'\rightarrow[0,1]}{\forall P\in\events'.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}

\noindent Then, Gleason's theorem guarantees that $\bar{\mu}$ has
a unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
In the rest of the letter, we will provide examples of quantum IVPMs
on $\events_{24}$, and show how a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
could be depending on different intervals~$\mathscr{I}$.

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that a well-behaved
quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
quantum IVPMs happen when mapping to other kind of intervals. For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation} 
\iota_1(x)=\begin{cases} 
\necess & \text{ if}x=1\text{ ;}\\ 
\imposs & \text{ if}x=0\text{ ;}\\ 
\unknown & \text{ otherwise.}
\end{cases}\label{eq:homomorphism-1} \end{equation}
We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.

Although the quantum IVPM listed above are all well-behaved, there
are some quantum IVPMs far from the Born rule. Consider $\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
defined by $\bar{\mu}(P)=\unknown$ for every projection~$P$. Since
every quantum probability measure is in the core of $\bar{\mu}$,
this measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question.

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{subequations}
\label{eq:non-Kernaghan}
\begin{eqnarray}
1 & = & f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1) \nonumber \\*
  &   & +f(1,0,0,1)\textrm{ ,}\\ 
1 & = & f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1) \nonumber \\*
  &   & +f(1,0,0,1)\textrm{ ,}\\ 
1 & = & f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,0,1,0)\textrm{ ,}\\ 
1 & = & f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,0,1,0)\textrm{ ,}\\ 
1 & = & f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1) \nonumber \\*
  &   & +f(1,1,-1,-1)\textrm{ ,}\\ 
1 & = & f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
1 & = & f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1) \nonumber \\*
  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
1 & = & f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,1,1,1)\textrm{ ,}\\ 
1 & = & f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1) \nonumber \\*
  &   & +f(1,1,1,1)\textrm{ .} 
\end{eqnarray}
\end{subequations}
\qed\end{example}

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
define a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
as follow. 
\begin{subequations}
\begin{eqnarray}
&   & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) \nonumber \\*
& = & \bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
&   & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) \nonumber \\*
& = & \bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
& & \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
\end{eqnarray}
\end{subequations}
To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check
\begin{subequations}
\begin{eqnarray}
&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right) \nonumber \\*
& \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
&           & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right) \nonumber \\*
& \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
\end{eqnarray}
\end{subequations}
for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.
This equation always holds because $\unknown$ is a subset of the
left-hand side of both of the equations.

Second, we will prove that $\bar{\mu}$ cannot correspond to any quantum
probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events_{24}\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem\footnote{\yutsung{Find all orthogonal basis of $\mathcal{T}_{24}$ and solve
the linear equations for Gleason's...}}, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

>>>>

\begin{abstract}
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision. {\small \par}
\item [{Method}] We model the idea of the finite precision measurement
as finite number of intervals, and replace quantum real-valued probability
measures by interval-valued ones.{\small \par}
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear. {\small \par}
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.{\small \par}
\end{description}
\end{abstract}

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{ if}x=1\text{ ;}\\
\imposs & \text{ if}x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
satisfying the following conditions because of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\
 &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\
 &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up equation~\ref{eq:Kernaghan}, we
will have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(-1,1,1,1)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(-1,1,1,1),(1,-1,1,-1),\nonumber \\
 &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in left-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the left-hand
side is a singleton set of an even integer while the right-hand side
is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.

\paragraph{Quantum IVPM and Real-valued Probability Measure}

Recall we model the idea of the finite precision measurement as IVPM.
Given a quantum IVPM, the natural question would be whether we are
able to refine precisely enough to determine the underlying unknown
quantum real-valued probability measure, i.e., a quantum state. This
leads to the definition of core:\begin{definition}A \emph{core} of
$\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation}
\iota_{1}(x)=\begin{cases}
\necess & \text{ if}x=1\text{ ;}\\
\imposs & \text{ if}x=0\text{ ;}\\
\unknown & \text{ otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
is a quantum IVPM, and we have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\circ$ denote function composition.

While Shapley proved a good enough classical IVPM always has a non-empty
core, and we haven't found any classical IVPM having an empty core,
there are some simple quantum IVPM which has an empty core.

\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}
Every classical convex interval-valued probability measure has a non-empty
core, where $\bar{\mu}$ is called convex if 
\begin{equation}
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
define a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$
as follow. \begin{subequations} 
\begin{eqnarray}
 &  & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})\nonumber \\*
 & = & \bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\
 &  & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})\nonumber \\*
 & = & \bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\
 &  & \bar{\mu}(P)=\unknown\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations} To verify $\bar{\mu}$ is a quantum IVPM, first
notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check \begin{subequations} 
\begin{eqnarray}
 &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\nonumber \\*
 & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
 &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\nonumber \\*
 & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
\end{eqnarray}
\end{subequations} for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
and $\ket{\psi_{2}}$. This equation always holds because $\unknown$
is a subset of the left-hand side of both of the equations.

Second, we will prove that $\bar{\mu}$ cannot correspond to any quantum
probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events_{24}\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}
